---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PipMet

<!-- badges: start -->

The PipMet package was developed to process begin-to-end metabolomic-based GC-MS data, with the automatized generation of pictures throughout the processing in high quality. Every input from the user is taken through pop-up windows.This package was first developed for the Brazilian National Biorenewables Laboratory (LNBR) from the Brazilian National Center for Research in Energy and Materials (CNPEM).

<!-- badges: end -->

## Installation

You can install the released version of PipMet from [GitHub](https://github.com) with:

``` {r, eval = FALSE}
devtools::install_github("AnnafCouto/PipMet")
```

The user may also install the package through Bioconductor repository:

``` {r, eval = FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("PipMet")
``` 

## Example

The package is constituted of two main functions with pre-set parameters and algorithms for GC-MS data processing. The `workData()` function reads, treats and process GC-MS sample data, with metabolite identification and quantification. The second one, `workLib()` provides a workflow for an internal library creation to be uploaded into NIST MS Search software for spectra annotation.

The package was thought to be the more friendly-user as possible, even though it runs in code lines. Therefore, when information is needed, pop-ups will appear so that the user can input them.

``` {r, eval=FALSE}
result <- workData(
   sample_dir = system.file("extdata", package = "PipMet"),
   metadata = system.file("extdata", "metadata.csv", package = "PipMet"),
   extension = ".mzXML",
   myDir = '~/',
   example = TRUE,
   pictures = TRUE
)
```


``` {r, eval=FALSE}
library(PipMet)
workLib(
   extension = ".mzML",
   myDir = '~/',
   example = TRUE,
)
```

Set 'pictures = TRUE' to generate pictures along the code.

For more information, see the package [vignette](vignettes/workData.Rmd).
